%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[a4paper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage{upquote}
\usepackage[T1]{fontenc}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}
{
  \vspace{-4pt}\scshape\raggedright\large
}
{}{0em}{}
[\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{#1 \vspace{-2pt}}
}

\newcommand{\resumeEducationHeading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2
      \end{tabular*}
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      #3 & #4
      \end{tabular*}
}

\newcommand{\resumeSubheading}[3]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2
      \end{tabular*}
      \textit{\small#3}
}

\newcommand{\resumeMiniheading}[2]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2
    \end{tabular*}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*, itemsep=6pt]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*, topsep=0ex]}
\newcommand{\resumeItemListEnd}{\end{itemize}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Weichen Ke} & Email: weichenzero@gmail.com\\
  darkforte.github.io $\Diamond$ www.linkedin.com/in/weichenzero/ & Mobile: (412)482-8717 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \begin{itemize}[leftmargin=*, itemsep=-10pt]
    \resumeEducationHeading
      {Carnegie Mellon University}{Pittsburgh, PA}
      {\textit{M.S. in Computer Science}}{2018.08 -- Present}
    
    \resumeEducationHeading
      {Peking University}{Beijing, China}
      {\textit{Research Assistant in Computer Science, TA of Algorithm Analysis}}{2016.09 -- 2018.06}
    
    \resumeEducationHeading
      {Beijing University of Technology}{Beijing, China}
      {\textit{Bachelor in Computer Science | GPA: 3.93/4.0, Rank: 1/44}} {2012.09 -- 2016.07}
  \end{itemize}
    
  %\resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Didi Chuxing}{2017.07 -- 2018.07}
      {Algorithm Research Intern at Smart Mobility Group/AI Labs}
      \resumeItemListStart
        \resumeItem
        {Designed a reinforcement learning based order dispatching strategy with Deep Q Network and pushed it online.}
        \resumeItem
        {Built an automated feature visualization pipeline with Hive on PySpark.}
        \resumeItem
        {Organized and presented several company-wide tutorials on Deep RL topics like A3C, TRPO, and DDPG etc.}
    \resumeItemListEnd
      
    \resumeSubheading
      {Microsoft Research Asia}{2015.07 -- 2016.07}
      {Research Intern at Software Analytics Group, Leader of project BigIN4}
      \resumeItemListStart
        \resumeItem
        {Proposed a novel algorithm for interactive approximate query processing on big data based on Tree Augmented Bayesian Network, and implemented it on Spark with Scala and Java.}
        \resumeItem
        {Deployed the platform to production cluster running on Hadoop, and analyzed more than 1TB data per day.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
  
%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeMiniheading{Flappy Bird AI based on Deep Reinforcement Learning }{2017.06}
        \resumeItemListStart
            \resumeItem {Designed the network architecture with Tensorflow.}
            \resumeItem {Implemented A3C algorithm from scratch, with asynchronous exploration and model updating using Python.}
        \resumeItemListEnd
    
    \resumeMiniheading{Parameter Server based on C\texttt{++} and MPI}{2017.06}
        \resumeItemListStart
            \resumeItem {Designed the master-coordinator-worker architecture and the communication protocol with Protobuf.}
            \resumeItem {Implemented the architecture with MPI that supports adding/removing workers dynamically.}
            \resumeItem {Implemented sparse parameter transmission to reduce messaging overhead.}
        \resumeItemListEnd
        
    \resumeMiniheading{Real-time Online Game: "Bomber Man Online" on C\texttt{++} and Direct2D}{2015.04}
        \resumeItemListStart
            \resumeItem {Designed the Client-Server architecture and the messaging protocol under IOCP.}
            \resumeItem {Implemented the game core from scratch and efficient game data access using STL with Visual Studio.}
            \resumeItem {Implemented lockstep multiplayer synchronization model with a mutex based thread scheduler.}
        \resumeItemListEnd
        
  \resumeSubHeadingListEnd

%-----------PUBLICATIONS-----------------
\section{Publication}
  \resumeItemListStart
    \resumeItem 
    {Qingwei Lin, \textbf{Weichen Ke}, Jian-Guang Lou, Hongyu Zhang, Kaixin Sui, Yong Xu, Ziyi Zhou, Bo Qiao, Dongmei Zhang. "BigIN4: Instant, Interactive Insight Identification for Multi-Dimensional Big Data", \textbf{SIGKDD 2018} (First Student Author) }
  \resumeItemListEnd

%-----------AWARDS-----------------
\section{Honors}
  \begin{itemize}[leftmargin=*, itemsep=-12pt]
    \resumeMiniheading{"Star of Tomorrow" Title {\normalfont(For MSRA interns with outstanding performance)}}{2016}
    \resumeMiniheading{Silver Medal of EC-Final Round of ACM-ICPC contest}{2015}
    \resumeMiniheading{IBM Scholarship and National Scholarship {\normalfont(For top 3 students in the dept.)}}{2014}
    \resumeMiniheading{Global Rank 18/1000\texttt{+}, China Rank 2/50\texttt{+} in IEEExtreme Programming Contest}{2013}
    \resumeMiniheading{Meritorious Winner of MCM}{2013}
  \end{itemize}

%--------PROGRAMMING SKILLS------------
\section{Skills}
  \begin{itemize}[leftmargin=*, itemsep=-3pt]
    \item{
      \textbf{Programming Languages}{: C\texttt{++}, Java, Python, Scala}
    }
    \item{
      \textbf{Framework \& Libraries}{: Hadoop, Spark, Hive, Protobuf, Tensorflow, Keras, XGBoost}
    }
    \item{
      \textbf{Methods \& Tools}{: Git, Latex, Linux}
    }
  \end{itemize}


%-------------------------------------------
\end{document}
